Magnitude of simple rules in investment strategies of algorithmic trading

### 2013-06-04 Article/Article20130603/tewi-paper-template.tex
Zmiana w wypisaniu wzoru, indeksy poprawione. Dodane enumerate do sytuacji.

  C_{mi} = (C_{i-m} + C_{i-m+1} + … + C_{i} ) / m; 

@@

At the moment of I bar closing, value can be compared with the Cmi average. Depending on the investor's beliefs about the existence of a particular trend are thus four possible decision-making situations:
1. If Ci  > Cmi  long position will be open
2. If Ci  > Cmi  short position will be open
3. If Ci  < Cmi  long position will be open
4. If Ci  < Cmi  short position will be open

@@

\begin{figure}[h]
 \centering
 \includegraphics[width=\textwidth]{Rysunek0_all2.eps}
 \caption{Symbolic quadrant of response (second line) for market movement (first line)}
\end{figure}
\FloatBarrier

>>>>

  C_{m_{i}} = \frac{C_{i-m} + C_{i-m+1} + … + C_{i}}{m}; 

@@

At the moment of I bar closing, value can be compared with the $C_{m_{i}}$ average. Depending on the investor's beliefs about the existence of a particular trend are thus four possible decision-making situations:
\begin{enumerate}
\item If $C_i  > C_{m_{i}}$  long position will be open,
\item If $C_i  > C_{m_{i}}$  short position will be open,
\item If $C_i  < C_{m_{i}}$  long position will be open,
\item If $C_i  < C_{m_{i}}$  short position will be open.
\end{enumerate}

@@

\begin{figure}[h!]
 \centering
 \includegraphics[width=\textwidth]{Rysunek0_all2.eps}
 \caption{Symbolic quadrant of response (second line) for market movement (first line)}
\end{figure}
\FloatBarrier
